A GPU Sonar Simulator for Automatic Target Recognition

### 2014-04-30 UAM2014/Article/article.tex
la2pdf commit - 2014:04:30	12:50:38	(Wed30.Apr)

To produce the sonar templates we assume a rough, isotropic surface that reflects energy equally in all directions. This permits us to use a Lambertian scattering model where the backscatter intensity depends only on the incidence angle~\cite{Zhang1999}. It does not consider observation angle or sound frequency, but the purpose of creating templates this is needed.

@@

The main advantage of a GPU-based simulator over a standard simulator is its ability to create templates incredibly fast. This makes it possible to tailor the templates more closely to an image as the parameters needed by the simulator can be directly estimated from the image. In a standard approach, on the other hand, a template library must be created beforehand from a limited set of parameter values. Hence, it may happen that no template in the library is a close fit of the object in the image even though the object actually is a target of interest.

@@

The standard and adaptive templates were then matched to the HISAS image. This is illustrated in Fig. 4a for a standard template and in Fig. 4b for an adaptive template. These images were created by segmenting the image and the templates into highlight, shadow, and background regions. The regions from a template were then laid on top of the regions of the image to illustrate how well these regions matched. From these figures, it was quite clear the adaptive template obtained a much closer fit to image than the standard template. This was also reflected in the correlation scores (which were created with the method described in \cite{Midelfart2010}) that were 0.613 for the standard template and 0.813 for the adaptive template. Hence, the standard approach was less likely to classify the cylinder in the image correctly as the standard templates were not created specifically for the target.

@@

>>>>

To produce the sonar templates we assume a rough, isotropic surface that reflects energy equally in all directions. This permits us to use a Lambertian scattering model where the backscatter intensity depends only on the incidence angle~\cite{Zhang1999}. It does not consider observation angle or sound frequency, but for the purpose of creating templates this is needed.

@@

Whenever conventional computer graphics processing can be used to 
GPUs are designed to provide the best possible graphics processing performance, and there large ecosystem of tools and libraries  available 
Using a GPU to drive a simulator is advantageous since

Using a GPU-based simulator is attractive since computer is an attractive solution as there are a  graphics traits. For one over a CPU-based standard simulator is two-fold: First is its ability to create templates incredibly fast. This makes it possible to tailor the templates more closely to an image as the parameters needed by the simulator can be directly estimated from the image. In a standard approach, on the other hand, a template library must be created beforehand from a limited set of parameter values. Hence, it may happen that no template in the library is a close fit of the object in the image even though the object actually is a target of interest.

@@

The standard and adaptive templates were then matched to the HISAS image. This is illustrated in Fig. \ref{overlay_cylinder} for a standard template and in Fig. \ref{overlay_cylinder_adaptive} for an adaptive template. These images were created by segmenting the image and the templates into highlight, shadow, and background regions. The regions from a template were then laid on top of the regions of the image to illustrate how well these regions matched. From these figures, it was quite clear the adaptive template obtained a much closer fit to image than the standard template. This was also reflected in the correlation scores (which were created with the method described in \cite{Midelfart2010}) that were 0.613 for the standard template and 0.813 for the adaptive template. Hence, the standard approach was less likely to classify the cylinder in the image correctly as the standard templates were not created specifically for the target.

@@

\section{Conclusion}

Modern GPUs are customized to perform computer graphics. Their theoretical peak performance is typically and order of magnitude higher than a CPU in a comparable price range. This performance can not always be achieved in practice, unless the algorithm can be adapted to use a well matured and optimized graphics processing API such as OpenGL. Our simulator uses OpenGL for most of the , then it makes little

Whether this performance can be achieved in practice 
Whenever conventional computer graphics processing can be used to 
GPUs are designed to provide the best possible graphics processing performance, and there large ecosystem of tools and libraries  available 
Using a GPU to drive a simulator is advantageous since
